\prefacesection{Acknowledgements}

\paragraph{}There are many people who helped me at some point during the course of my studies here at McMaster University.  First and foremost, I would like to thank both of my supervisors, Dr. Sue Becker and Dr. Laurel Trainor, for being exemplary mentors.  I have grown so much in the past few years as a result of their guidance, and for this I am very grateful.  I must also extend a thank you to Dr. Larry Roberts, for his generosity in lending his lab space to me to perform hearing evaluations, thus allowing me to recruit participants for my experiments.  I surely would not have had the same success without my labmates, who often provided me with helpful suggestions when I presented at lab meetings, and made the lab a fun place to work.  Thank you to Dave Thompson, and Dan Bosnyak for your technical support, and Elaine Whiskin, for always lending a hand and taking care of all the lab essentials.  I am thankful for the considerable assistance I received from two undergraduate assistants, Ranya Amirthamanoharan, and Katelyn Muir, who helped run participants through many experiments.

I must also thank the industry partner who I collaborated with during this project, VitaSound Audio Inc., for the time they spared to meet with me to provide guidance on how to properly conduct my experiments.  From VitaSound in particular, I would like to thank Gora Ganguli, Philippe Pango, Karl Wiklund, Mario Augustyniak, Sam Mok, Karen Lalonde, and Clare Daley for their assistance throughout the course of the project, and their contribution of resources.  I am deeply grateful for the assistance of Peter Chmielewski, the hearing instrument specialist who I worked with throughout the study, who put in many hours programming the hearing aids for the participants in all of my experiments, as well as consulted with the participants, and provided me with a basic, practical education of hearing aids.

Last, I thank my Mom and Dad for their consistent support, encouragement, wisdom, and love, and my brothers, David, Neil, and Daniel, for paving the path.

This work was funded by NSERC 5-38048 and MITACS 5-98517. 