\begin{appendices}

%Insert computational algorithms for the mistuned harmonic, timbre perception, gap detection.

\chapter{Sound Quality Questionnaire}
\singlespacing
\begin{enumerate}
\item How clear does music sound with the hearing aids you are \textit{currently} wearing? \\
1 (unclear) 2 (moderately unclear) 3 (neither clear nor unclear) 4 (moderately clear) 5 (clear)
\item How pleasant does music sound with the hearing aids you are \textit{currently} wearing? \\
1 (unpleasant) 2 (moderately unpleasant) 3 (average) 4 (moderately pleasant) 5 (pleasant)
\item How natural does music sound with the hearing aids you are \textit{currently} wearing? \\
1 (unnatural) 2 (moderately unnatural) 3 (average) 4 (moderately natural) 5 (natural)
\item How full does music sound with the hearing aids you are \textit{currently} wearing? \\
1 (thin) 2 (moderately thin) 3 (neither thin nor full) 4 (moderately full) 5 (full)
\end{enumerate}

\noindent For the following conditions, rate how pleasant the listening experience is while wearing the hearing aids you are \textit{currently} wearing: \\
1 = unpleasant \\
2 = moderately unpleasant \\
3 = average \\
4 = moderately pleasant \\
5 = pleasant
\begin{enumerate}
\item Listening to a small live performance (solo/small group).
\item Listening to a large live performance (concert/orchestra).
\item Listening to TV programs.
\item Listening on the telephone.
\item Listening to another talker in quiet.
\item Listening to a car radio.
\item Listening to another talker amongst competing talkers.
\item Listening to speech in an auditorium/gymnasium.
\item Listening to speech/music at the cinema.
\item Listening to your favourite recordings of your favourite music.
\end{enumerate}
\doublespacing

\end{appendices}